### 2019-02-05 thesis_report/introduction.tex
added novelty of thesis

	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories.
	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.

	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
	Finally, in Chapter \ref{chap:conclusion}, we discuss the findings of this thesis, as well as an outlook on further research to be performed.

>>>>

\section{Thesis structure}
	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
	Additionally, the reduction of the Majorana decay length allows for shorter systems to produce a higher magnitude of seperation, which is favorable because the coherence length of a material sets a limit for the device size.

	Furthermore, we try to establish the working mechanism behind the improvements: we hypothesize that the gap improvement is the result of the elimination of long trajectories.
	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.

	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
	Finally, in Chapter \ref{chap:conclusion} we discuss the findings of this thesis, as well as provide an outlook on further research to be performed.

### 2019-02-05 thesis_report/theory.tex
added novelty of thesis

    \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/pientka_system}
    \caption{System overview of the paper by Pientka et. al.~\cite{pientka_topological_2017}
    A magnetic field is directed along the length of the strip, and the separation between the two superconductors is $W$.
    A superconducting phase difference lifts the mirror-symmetry otherwise present in the system, allowing for the system to enter the topological phase.
    In a finite system of size $L$, Majoranas (represented by $\gamma$) appear at the ends of the strip.
    Note that in this system, the two superconducting slabs (blue) are deposited onto the semiconductor, proximitizing the 2DEG below.
    By doing so, the underlying areas become the effective superconductors, and the entire system is defined within the semiconductor crystal, ensuring virtually perfect NS interfaces.}
    \label{fig:pientka_system}
    \end{figure}

@@

        \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
        \caption{Topological phase diagram as a function of superconducting phase and magnetic field.~\cite{pientka_topological_2017}
        The diagram has a diamond shape, repeating along the magnetic field axis with a period equal to $2 E_\text{Th}$.
        }
        \label{fig:pientka_phase_diagram}
        \end{figure}

@@

        \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\columnwidth]{figures/pientka_bandstructure}
        \caption{Bandstructure of a straight SNS system~\cite{pientka_topological_2017}.
        Note that the gap is minimized when $k_x=k_{F,1}$ and $k_x=k_{F,2}$, which correspond to the Rashba/Zeeman split Fermi momenta.}
        \label{fig:pientka_bandstructure}
        \end{figure}

>>>>

    \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/pientka_system}
    \caption{System overview of the paper by Pientka et. al.~\cite{pientka_topological_2017}
    A magnetic field is directed along the length of the strip, and the separation between the two superconductors is $W$.
    A superconducting phase difference lifts the mirror-symmetry otherwise present in the system, allowing for the system to enter the topological phase.
    In a finite system of size $L$, Majoranas (represented by $\gamma$) appear at the ends of the strip.
    Note that in this system, the two superconducting slabs (blue) are deposited onto the semiconductor, proximitizing the 2DEG below.
    By doing so, the underlying areas become the effective superconductors, and the entire system is defined within the semiconductor crystal, ensuring virtually perfect NS interfaces.\\
    Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
    }
    \label{fig:pientka_system}
    \end{figure}

@@

        \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
        \caption{Topological phase diagram as a function of superconducting phase and magnetic field.
        The diagram has a diamond shape, repeating along the magnetic field axis with a period equal to $2 E_\text{Th}$.\\
        Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
        }
        \label{fig:pientka_phase_diagram}
        \end{figure}

@@

        \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\columnwidth]{figures/pientka_bandstructure}
        \caption{Bandstructure of a straight SNS system.
        Note that the gap is minimized when $k_x=k_{F,1}$ and $k_x=k_{F,2}$, which correspond to the Rashba/Zeeman split Fermi momenta.\\
        Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
        }
        \label{fig:pientka_bandstructure}
        \end{figure}
